Verification in Isabelle/HOL of a Set-based Algorithm for Computing Strongly Connected Components

### 2022-09-15 cpp/submission.tex
Added some examples in the introduction

They are also heavily used in critical domains that indirectly affect us, such as model checking.
Indeed, as model checking involves exhaustive exploration of graphs of states, it is important to have efficient -- and correct -- algorithms to perform different operations such as the computation of strongly connected components.

>>>>

Graphs are also heavily used in domains to which we are indirectly linked, such as model checking and formal verification, which find applications in the safety of critical systems such as nuclear, aerospace, aeronautics or railways.

Since model checking involves exhaustive exploration of graphs of states, it is important to have efficient -- and correct -- algorithms to perform different operations such as the computation of strongly connected components.
